---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# speechiespeech

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of speechiespeech is to allow a user to easily parse text from public
websites with a variety of source types and perform basic text mining and analysis 
functions including tokenizing a text file, performing and visualizing sentiment
analysis, and analyzing relative frequency of words across a set of source 
documents. 

In its current version, speechiespeech supports the parsing of text from html pages
provided input of an appropriate css selector. Development is required to make
css selection more user friendly.

Current development efforts focus on parsing of text from pdf source files, with
publicly accessible Supreme Court slip opinion files providing prototype
data sources.

## Installation

You can install the development version of speechiespeech from GitHub with:

``` r
devtools::install_github("speechiespeech")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(speechiespeech)
## basic example code
```


